The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-05-25 Paper.Rmd
adding description for effect on extrisk section

@@

    * For LC model, as expected, when extinction risk calculated after $25$ years, was plotted against each $d$ (=degree of dispersion) we varied, we found that extinction risk was higher for data came from left tail dependent environmental fluctuations than right tail dependent one. [see first plot of Fig. \ref{SM-fig_risk_local_disp} and Fig. \ref{SM-fig_risk_global_disp}]

@@

    * For ricker model when extinction risk calculated after $25$ years, was plotted against each $d$ (=degree of dispersion) we varied, we found that extinction risk was higher for data came from left tail dependent environmental fluctuations than right tail dependent one upto $r=0.7$. For $r>0.7$, extinction risk is greater for data came from right tail dependent environmental fluctuations. [see Fig. \ref{SM-fig_risk_local_disp} - \ref{SM-fig_risk_global_disp}]

@@

With increasing $numlocs$ from $5$ to $25$, extinction risk decreased [for a fixed $d$] ; [see Fig. \ref{SM-fig_risk_numlocs_effect_local_disp} - Fig. \ref{SM-fig_risk_numlocs_effect_global_disp}] for both model.

>>>>

In order to study the effects of non-gaussian copula structure on extinction risk for population of a species at different locations with different dispersal rules, we examined the following generalized multiple patch model where local population dynamics at each patch were governed by the Lewton-Cohen model ($r=0$) or Ricker model ($r \neq 0$) as the case may be;
<!--did I write correct spelling for lewton model?-->

\begin{equation}\label{eq.extrisk_model}
P(t+1) = \exp\left [  r\left ( 1-\frac{P(t)}{K} \right ) + \epsilon(t) \right ] P(t)
\end{equation}

$r$ is the liner growth rate and $K$ is the carrying capacity of the environment. $\epsilon$ is the environmental noise which may take strong right tail (or left tail) dependence. We then considered each population $P(t+1)$ was updated depending upon $D$, the dispersal matrix. $D$ can take either forms; one case when each population patch on a linear chain interacted with its two nearest neighbors (we called it local dispersion) or when any patch can interact with the rest of all (we called it as global dispersion). We simulated Eq. \ref{eq.extrisk_model} for $10000$ simulations and calculated extinction risk after $25$ years with different possibilities (for code see [mydispersal.R](https://github.com/sghosh89/BIVAN/blob/master/mydispersal.R)) and summarized our findings as follows;

@@

    * For LC model, as expected, when extinction risk calculated after $25$ years, was plotted against each varying $d$ (=degree of dispersion), we found that extinction risk was higher for data came from left tail dependent environmental fluctuations than right tail dependent one. [see first plot of Fig. \ref{SM-fig_risk_local_disp} and Fig. \ref{SM-fig_risk_global_disp}]

@@

    * For ricker model when extinction risk calculated after $25$ years, was plotted against each varying $d$ (=degree of dispersion), we found that extinction risk was higher for data came from left tail dependent environmental fluctuations than right tail dependent one upto $r=0.7$. For $r>0.7$, extinction risk is greater for data came from right tail dependent environmental fluctuations. [see Fig. \ref{SM-fig_risk_local_disp} - \ref{SM-fig_risk_global_disp}]

@@

With increasing number of patches from $5$ to $25$, extinction risk decreased [for a fixed $d$] ; [see Fig. \ref{SM-fig_risk_numlocs_effect_local_disp} - Fig. \ref{SM-fig_risk_numlocs_effect_global_disp}] for both model.
